Minimal Positive Influence of Helpline Efforts on Reduction of Homeless Death in Toronto

### 2024-03-12 paper/paper.qmd
Edited the result section

-   there exist a net negative correlation between helpline efforts and
    homeless death count in Toronto

@@

@@

Hypothesis 1: - null hypothesis: true effect of total_calls_coded = 0 -
use t-stat to check at 95% significance level

Hypothesis 2: - null hypothesis: true effect of referred = 0 - use
t-stat to check at 95% significance level

Hypothesis 3: - null hypothesis: true effect of referred = 0 - use
t-stat to check at 95% significance level

>>>>

-   Under the Gaussian regression model, @fig-total-coded illustrates a
    fitted line that estimates the linear relationship between the
    number of total calls coded and homeless death count in Toronto. The
    graph suggest that there exist a net negative correlation between
    the two variable. According to the graph, homeless death count
    decrease as total number of calls coded increase. The significance
    of this relationship is discussed below in in the model summary
    table.

@@

-   The model summary table, @tbl-modelresults, displays the coefficient
    values of the predictor variables against response variable:
    homeless death count in Toronto. Coefficients of predictors indicate
    their influence against the response variable. For example, the
    column on the left shows that, under Model 1, every 1 additional
    helpline call coded and decrease the homeless death count by 0.0003.
    The ***+p \<...*** section at the bottom of the table represents
    statistically significance of the coefficient values. As indicated
    by the ***+p\<...*** legend, the coefficients with 1 \*, coefficient
    is significant at 95% confidence level; for \*\*, coefficient is
    significant at 99% confidence level, and so on. However, as we can
    see from the table below, no \* exists for the coefficients in both
    models.

@@
